Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-20 docs/manuscript/manuscript.tex
Advanced Correlation Graph of Modes of Transportation and Time

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{correlation-basic}
  \caption{Correlation graph of numerical variables}
  \label{fig:year}
\end{figure}
As we continued to study further upon the correlations of the variables, we used more advanced correlation graphs to determined their p value and to see relationship between different categorical variables is shown in Figure 3, which again indicates greater detailed comparison between the variables. Households with improved water source on the premises (iwsp) has strong relationship with  households with basic water service (basw) of .84 and p value of less than 0.001. Also, we learned and discovered that Households using an unimproved water source (uiws) have a positive relationship with Households using an unprotected well water (uwel), Households using an unprotected spring (uspr), and Households using surface water (surw) with p value of less than 0.001 as well. These relationships justify the necessity to research further if the particular water accessibility variables can increase accessibility of particular water sources in order to reach the universal access to water by 2030, as proposed in the SDGs.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{adv-cor-plot}
  \caption{Correlation graph of numerical variables}
  \label{fig:year}
\end{figure}
Additionally, we wanted to explore if the modes of transportation variables have any relationship with potential water variables. Therefore, we investigated by developing more correlation plots relating transportation variables with water accessibility variables which is shown in Figure .

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{transportation-time}
  \caption{Correlation graph of numerical variables}
  \label{fig:year}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{spider-plot}
  \caption{Spider plots of water accessibility variables by typology}
  \label{fig:spider}
\end{figure}
\subsection*{Model results}

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{correlation-basic}
  \caption{Correlation Graph of Numerical Variables}
  \label{fig:year}
\end{figure}
As we continued to study further upon the correlations of the variables, we used more advanced correlation graphs to determined their p value and to see relationship between different categorical variables is shown in Figure 3, which again indicates greater detailed comparison between the variables. Households with improved water source on the premises (iwsp) has strong relationship with  households with basic water service (basw) of .84 and p value of less than 0.001. Also, we learned and discovered that Households using an unimproved water source (uiws) have a positive relationship with Households using an unprotected well water (uwel), Households using an unprotected spring (uspr), and Households using surface water (surw) with p value of less than 0.001 as well. These relationships justify the necessity to research further if the particular water accessibility variables can increase accessibility of particular water sources in order to reach the universal access to water by 2030, as proposed in the SDGs.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{adv-cor-plot}
  \caption{Advanced Correlation Graph of Numerical Variables}
  \label{fig:year}
\end{figure}
Additionally, we wanted to explore if the modes of transportation variables have any relationship with potential water variables. Therefore, we investigated by developing more correlation plots relating transportation variables with water accessibility variables which is shown in Figure 4,5,6 .

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{transportation-time}
  \caption{Advanced Correlation Graph of Modes of Transportation and Time}
  \label{fig:year}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{spider-plot}
  \caption{Spider Plot of Water Accessibility Variables by Typology}
  \label{fig:spider}
\end{figure}
\subsection*{Model results}
